title: "Lab6Package"
authors: Marketos Damigos (marda352) & Christoforos Spyretos (chrsp415)
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Lab6Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

```{r}
library(Lab6package)
library(parallel)
```

##  Introduction

Knapsack algorithm implented with brute force, greedy and dynamic solutions.

## Data Initalazation
```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))

set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```

## Brute Force Search

```{r}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)

brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500)

brute_force_knapsack(x = knapsack_objects[1:8,], W = 2000)

brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000)
```
#### Question 1
How much time does it takes to run the algorithm for n = 16 objects?

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 2000))
```

It took on average 1.146sec.

## Dynamic Programming

```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)

knapsack_dynamic(x = knapsack_objects[1:12,], W = 3500)

knapsack_dynamic(x = knapsack_objects[1:8,], W = 2000)

knapsack_dynamic(x = knapsack_objects[1:12,], W = 2000)
```

#### Question 2
How much time does it takes to run the algorithm for n = 500 objects?

```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```

It took 4.049sec.

## Greedy Heuristic

```{r}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)

greedy_knapsack(x = knapsack_objects[1:1200,], W = 2000)
```

#### Question 3
How much time does it takes to run the algorithm for n = 1000000 objects?

```{r}
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500))
```

It took 1.520sec.

#### Question 4
What performance gain could you get by trying to improving your code?

After running profvis() for our brute force implementation we change from using lapply to sapply.

#### Question 5
What performance gain could you get by parallelizing brute force search?

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:20,], W = 2000))
system.time(brute_force_knapsack(x = knapsack_objects[1:20,], W = 2000, parallel = TRUE))
```

It took 5.572sec for the parallel version and 12.919sec for the normal version, which is approximatelly 2.5 times faster.






